\raggedright
\begin{thebibliography}{bla}

\bibitem{YFullMutationRate} Dmitry Adamov, Vladimir Guryanov,
Sergey Karzhavin, Vladimir Tagankin, Vadim Urasin.
\emph{\href{http://rjgg.molgen.org/index.php/RJGGRE/article/view/151}
{Defining a New Rate Constant for Y-Chromosome SNPs based on Full Sequencing Data}}.
The Russian Journal of Genetic Genealogy
(\foreignlanguage{russian}{Русская версия}),
Vol 6, No 2 (2014)/Vol 7, No 1 (2015).

\bibitem{Fels78} Joseph Felsenstein,
\emph{\href{http://sysbio.oxfordjournals.org/content/27/4/401}
{Cases in which Parsimony or Compatibility Methods will be Positively Misleading}},
Systematic Zoology 27 (4): 401--410, 1978,
\href{http://dx.doi.org/10.1093/sysbio/27.4.401}{doi: 10.1093/sysbio/27.4.401}.

\bibitem{Ham15} David Hamilton,
\emph{\href{http://biorxiv.org/content/early/2015/06/19/020933}
{An accurate genetic clock}},
bioRxiv preprint, first posted online June 15, 2015,
\href{http://dx.doi.org/10.1101/020933}{doi: 10.1101/020933}.

\bibitem{ISOGGTreeR} ISOGG,
\emph{\href{http://www.isogg.org/tree/ISOGG_HapgrpR.html}
{Y-DNA Haplogroup R and its Subclades}}.
Date visited: 2015-10-05.

\bibitem{Kly09} Anatole A. Klyosov,
\emph{\href{http://www.jogg.info/52/files/Klyosov1.pdf}
{DNA Genealogy, Mutation Rates, and Some Historical
Evidence Written in Y-Chromosome, Part I:  Basic Principles and
the Method}}.
Journal of Genetic Genealogy, 5(2):186-216, 2009.

\bibitem{ht35Tree} Sergey Malyshev,
\emph{\href{https://www.familytreedna.com/groups/ht-3-5new/about/results}
{R1b-M269 (P312- U106-) DNA Project (aka ht35 Project) Phylogenetic Tree}}.
R1b-M269 (P312- U106-) DNA Project, Date visited: 2015-10-05.

\bibitem{PhyloageSourceDoc} Dirk Struve,
\emph{\href{https://godoc.org/github.com/yogischogi/phyloage/phylotree}
{Phyloage source code documentation}}, GoDoc, 2016.

\bibitem{Phylofriend} Dirk Struve,
\emph{\href{https://github.com/yogischogi/phylofriend/}{Phylofriend,
a program to calculate genetic distances}}.
Google Project Hosting, 2014; GitHub, 2015.

\bibitem{PhylofriendUserGuide} Dirk Struve,
\emph{\href{https://github.com/yogischogi/phylofriend/blob/master/doc/phylofriend.pdf?raw=true}
{Phylofriend User Guide}}.
Google Project Hosting, 2014; GitHub, 2015.

\bibitem{Wiki-Maximum_parsimony} Wikipedia,
\emph{\href{https://en.wikipedia.org/wiki/Maximum_parsimony_\%28phylogenetics\%29}
{Maximum parsimony}}.
Date accessed: 2016-03-28.

\bibitem{YFullTree} YFull,
\emph{\href{http://yfull.com/tree/}{YFull Phylogenetic Tree}}.
Date visited: 2016-03-01.

\end{thebibliography}
